---
bibliography: references.bib
csl: https://www.zotero.org/styles/chicago-author-date
citeproc: true

lang: en-US
number-sections: false
format-links: false

execute:
  echo: false
  message: false

format:

  # ============================================================
  # PDF — LATEX / XELATEX
  # ============================================================

  pdf:
    pdf-engine: xelatex
    documentclass: article
    fontsize: 12pt
    papersize: letter
    mainfont: "Times New Roman"

    indent: true
    block-headings: false

    geometry:
      - margin=1in

    hyperrefoptions:
      - hidelinks

    keep-tex: true

    include-in-header:
      text: |
        \usepackage{setspace}
        \usepackage{fancyhdr}
        \usepackage{titlesec}
        \usepackage{indentfirst}

        % ========================================================
        % BODY
        % ========================================================

        \doublespacing

        \setlength{\parindent}{0.5in}
        \setlength{\parskip}{0pt}

        % ========================================================
        % PAGE NUMBERS
        %
        % Title page:
        %   no visible number
        %
        % First actual text page:
        %   Arabic page 1, upper right
        % ========================================================

        \setlength{\headheight}{15pt}

        \pagestyle{fancy}
        \fancyhf{}
        \fancyhead[R]{\thepage}

        \renewcommand{\headrulewidth}{0pt}
        \renewcommand{\footrulewidth}{0pt}

        \fancypagestyle{plain}{
          \fancyhf{}
          \fancyhead[R]{\thepage}
          \renewcommand{\headrulewidth}{0pt}
          \renewcommand{\footrulewidth}{0pt}
        }

        % ========================================================
        % FIVE-LEVEL HEADING SYSTEM
        %
        % Level 1 = centered, bold
        % Level 2 = centered, regular
        % Level 3 = flush left, italic
        % Level 4 = flush left, regular
        % Level 5 = run-in, italic, terminal period
        % ========================================================

        \titleformat{\section}[block]
          {\normalfont\normalsize\bfseries\centering}
          {}
          {0pt}
          {}

        \titleformat{\subsection}[block]
          {\normalfont\normalsize\centering}
          {}
          {0pt}
          {}

        \titleformat{\subsubsection}[block]
          {\normalfont\normalsize\itshape}
          {}
          {0pt}
          {}

        \titleformat{\paragraph}[block]
          {\normalfont\normalsize}
          {}
          {0pt}
          {}

        \titleformat{\subparagraph}[runin]
          {\normalfont\normalsize\itshape}
          {}
          {0pt}
          {}
          [.]

        % ========================================================
        % HEADING SPACING
        % ========================================================

        \titlespacing{\section}
          {0pt}
          {\baselineskip}
          {\baselineskip}

        \titlespacing{\subsection}
          {0pt}
          {\baselineskip}
          {\baselineskip}

        \titlespacing{\subsubsection}
          {0pt}
          {\baselineskip}
          {\baselineskip}

        \titlespacing{\paragraph}
          {0pt}
          {\baselineskip}
          {\baselineskip}

        \titlespacing{\subparagraph}
          {0pt}
          {\baselineskip}
          {0.5em}

        % ========================================================
        % BLOCK QUOTATIONS
        %
        % Single spaced internally.
        % 0.5-inch left indent.
        % Same 12-point type.
        % ========================================================

        \renewenvironment{quote}
          {
            \par
            \addvspace{\baselineskip}
            \begin{singlespace}
            \begin{list}{}{%
              \setlength{\leftmargin}{0.5in}%
              \setlength{\rightmargin}{0in}%
              \setlength{\topsep}{0pt}%
              \setlength{\partopsep}{0pt}%
              \setlength{\parsep}{0pt}%
              \setlength{\itemsep}{0pt}%
            }
            \item\relax
          }
          {
            \end{list}
            \end{singlespace}
            \par
            \addvspace{\baselineskip}
          }

        % ========================================================
        % REFERENCES
        %
        % 0.5-inch hanging indent.
        % CSL controls spacing between entries.
        % ========================================================

        \setlength{\cslhangindent}{0.5in}

        \renewenvironment{CSLReferences}[2]
          {\begin{list}{}{%
            \setlength{\itemindent}{0pt}%
            \setlength{\leftmargin}{0pt}%
            \setlength{\rightmargin}{0pt}%
            \setlength{\parsep}{0pt}%
            \setlength{\topsep}{0pt}%
            \setlength{\partopsep}{0pt}%
            \ifodd #1%
              \setlength{\leftmargin}{\cslhangindent}%
              \setlength{\itemindent}{-1\cslhangindent}%
            \fi%
            \setlength{\itemsep}{#2\baselineskip}%
          }}
          {\end{list}}

  # ============================================================
  # MICROSOFT WORD
  #
  # IMPORTANT:
  #
  # cmos-reference.docx MUST be in the same directory.
  #
  # Create a Pandoc reference file initially with:
  #
  # quarto pandoc -o cmos-reference.docx \
  #   --print-default-data-file reference.docx
  #
  # Then modify its styles in Word.
  #
  # REQUIRED WORD DOCUMENT SETTINGS
  #
  # Page:
  #   Letter, 8.5 x 11
  #   1-inch margins
  #
  # Header:
  #   Different First Page = ON
  #   first-page header = empty
  #   normal header = page number right aligned
  #
  # Numbering:
  #   arrange numbering so physical page 2 displays Arabic 1
  #
  # Normal:
  #   Times New Roman
  #   12 pt
  #   double line spacing
  #   first-line indent = 0.5 inch
  #   0 pt before
  #   0 pt after
  #
  # Body Text:
  #   same as Normal
  #
  # First Paragraph:
  #   same as Normal
  #
  # Heading 1:
  #   TNR 12
  #   bold
  #   centered
  #   double spaced
  #
  # Heading 2:
  #   TNR 12
  #   regular
  #   centered
  #   double spaced
  #
  # Heading 3:
  #   TNR 12
  #   italic
  #   flush left
  #   double spaced
  #
  # Heading 4:
  #   TNR 12
  #   regular
  #   flush left
  #   double spaced
  #
  # Block Text:
  #   TNR 12
  #   single spaced
  #   left indent = 0.5 inch
  #   no first-line indent
  #
  # Bibliography:
  #   TNR 12
  #   single spaced
  #   hanging indent = 0.5 inch
  #   one blank line between entries
  #
  # CMOS Title:
  #   TNR 12
  #   regular
  #   centered
  #   double spaced
  #   no indent
  #   approximately 2.67 inches before
  #   approximately 2.67 inches after
  #
  # CMOS Title Info:
  #   TNR 12
  #   regular
  #   centered
  #   double spaced
  #   no indent
  #
  # CMOS References Heading:
  #   TNR 12
  #   regular
  #   centered
  #   single spaced
  #   no indent
  #   approximately two blank lines after
  # ============================================================

  docx:
    toc: false
    reference-doc: cmos-reference.docx

  # ============================================================
  # OPENDOCUMENT / LIBREOFFICE
  #
  # Content and page breaks will work.
  #
  # For exact ODT styling, use the same approach as Word with:
  #
  # reference-doc: cmos-reference.odt
  #
  # ============================================================

  odt:
    toc: false

  # ============================================================
  # HTML
  # ============================================================

  html:
    toc: false
    theme: default
    mainfont: "Times New Roman"
    fontsize: 12pt
    linestretch: 2
    page-layout: article

    include-in-header:
      text: |
        <style>

        html,
        body {
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          line-height: 2;
          color: black;
          background: white;
        }

        main.content,
        #quarto-content {
          max-width: 6.5in;
          margin-left: auto;
          margin-right: auto;
        }

        p {
          margin-top: 0;
          margin-bottom: 0;
          text-indent: 0.5in;
        }

        /* TITLE PAGE */

        .cmos-title-page {
          box-sizing: border-box;
          min-height: 9in;
          padding-top: 2.67in;
          text-align: center;
          break-after: page;
          page-break-after: always;
        }

        .cmos-title-page p,
        .cmos-title-page div {
          text-indent: 0;
        }

        .cmos-paper-title {
          margin: 0 0 2.67in 0;
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          font-weight: normal;
          font-style: normal;
          line-height: 2;
          text-align: center;
        }

        .cmos-paper-info {
          margin: 0;
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          font-weight: normal;
          font-style: normal;
          line-height: 2;
          text-align: center;
        }

        /* HEADINGS */

        h1,
        h2,
        h3,
        h4,
        h5 {
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          line-height: 2;
          color: black;
          border: none;
          padding: 0;
          margin-top: 1em;
          margin-bottom: 1em;
        }

        h1 {
          text-align: center;
          font-weight: bold;
          font-style: normal;
        }

        h2 {
          text-align: center;
          font-weight: normal;
          font-style: normal;
        }

        h3 {
          text-align: left;
          font-weight: normal;
          font-style: italic;
        }

        h4 {
          text-align: left;
          font-weight: normal;
          font-style: normal;
        }

        h5 {
          text-align: left;
          font-weight: normal;
          font-style: italic;
        }

        /* BLOCK QUOTATIONS */

        blockquote {
          margin-top: 1em;
          margin-bottom: 1em;
          margin-left: 0.5in;
          margin-right: 0;
          padding: 0;
          border-left: none;
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          line-height: 1;
          color: black;
        }

        blockquote p {
          text-indent: 0;
        }

        /* REFERENCES */

        .cmos-references-heading {
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          font-weight: normal;
          font-style: normal;
          line-height: 1;
          text-align: center;
          margin-top: 0;
          margin-bottom: 2em;
        }

        #refs,
        #refs .csl-bib-body {
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          line-height: 1;
        }

        #refs .csl-entry {
          margin-left: 0.5in;
          text-indent: -0.5in;
          margin-top: 0;
          margin-bottom: 1em;
        }

        </style>

  # ============================================================
  # EPUB
  # ============================================================

  epub:
    epub-title-page: false

    include-in-header:
      text: |
        <style>

        body {
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          line-height: 2;
        }

        p {
          margin-top: 0;
          margin-bottom: 0;
          text-indent: 0.5in;
        }

        .cmos-title-page {
          min-height: 9in;
          padding-top: 2.67in;
          text-align: center;
          break-after: page;
          page-break-after: always;
        }

        .cmos-title-page p,
        .cmos-title-page div {
          text-indent: 0;
        }

        .cmos-paper-title {
          margin-bottom: 2.67in;
          text-align: center;
          line-height: 2;
        }

        .cmos-paper-info {
          text-align: center;
          line-height: 2;
        }

        h1,
        h2,
        h3,
        h4,
        h5 {
          font-family: "Times New Roman", Times, serif;
          font-size: 12pt;
          line-height: 2;
          margin-top: 1em;
          margin-bottom: 1em;
        }

        h1 {
          text-align: center;
          font-weight: bold;
        }

        h2 {
          text-align: center;
          font-weight: normal;
        }

        h3 {
          text-align: left;
          font-weight: normal;
          font-style: italic;
        }

        h4 {
          text-align: left;
          font-weight: normal;
          font-style: normal;
        }

        h5 {
          text-align: left;
          font-weight: normal;
          font-style: italic;
        }

        blockquote {
          margin-left: 0.5in;
          margin-right: 0;
          padding: 0;
          border: none;
          line-height: 1;
        }

        blockquote p {
          text-indent: 0;
        }

        .cmos-references-heading {
          text-align: center;
          line-height: 1;
          margin-bottom: 2em;
        }

        #refs,
        #refs .csl-bib-body {
          line-height: 1;
        }

        #refs .csl-entry {
          margin-left: 0.5in;
          text-indent: -0.5in;
          margin-bottom: 1em;
        }

        </style>

  # ============================================================
  # TYPST PDF
  # ============================================================

  typst:
    papersize: us-letter
    mainfont: "Times New Roman"
    fontsize: 12pt
    linestretch: 2

    margin:
      top: 1in
      bottom: 1in
      left: 1in
      right: 1in

    include-in-header:
      text: |
        #show heading.where(level: 1): set align(center)
        #show heading.where(level: 1): set text(
          size: 12pt,
          weight: "bold",
          style: "normal"
        )

        #show heading.where(level: 2): set align(center)
        #show heading.where(level: 2): set text(
          size: 12pt,
          weight: "regular",
          style: "normal"
        )

        #show heading.where(level: 3): set text(
          size: 12pt,
          weight: "regular",
          style: "italic"
        )

        #show heading.where(level: 4): set text(
          size: 12pt,
          weight: "regular",
          style: "normal"
        )

        #show heading.where(level: 5): set text(
          size: 12pt,
          weight: "regular",
          style: "italic"
        )

---

<!-- ============================================================
TITLE PAGE — LATEX PDF
=============================================================== -->

::: {.content-visible when-format="pdf"}

```{=latex}
\begin{titlepage}

\thispagestyle{empty}

% Title approximately one-third down the physical page.

\vspace*{0.30\textheight}

{\centering

Your Paper Title\par

% Purdue says the identifying information should appear
% "several lines later."
%
% Eight double-spaced baselines is being used as a visual
% implementation of the sample, not as an independent
% Chicago rule.

\vspace{8\baselineskip}

Your Name\par
Course Number: Course Name\par
Month Day, Year\par

}

\end{titlepage}

% First page of actual text = page 1.

\setcounter{page}{1}
```

:::


<!-- ============================================================
TITLE PAGE — MICROSOFT WORD
=============================================================== -->

::: {.content-visible when-format="docx"}

::: {custom-style="CMOS Title"}
Your Paper Title
:::

::: {custom-style="CMOS Title Info"}
Your Name  
Course Number: Course Name  
Month Day, Year
:::

{{< pagebreak >}}

:::


<!-- ============================================================
TITLE PAGE — ODT
=============================================================== -->

::: {.content-visible when-format="odt"}

::: {custom-style="CMOS Title"}
Your Paper Title
:::

::: {custom-style="CMOS Title Info"}
Your Name  
Course Number: Course Name  
Month Day, Year
:::

{{< pagebreak >}}

:::


<!-- ============================================================
TITLE PAGE — HTML / EPUB
=============================================================== -->

::: {.content-visible when-format="html"}

::: {.cmos-title-page}

::: {.cmos-paper-title}
Your Paper Title
:::

::: {.cmos-paper-info}
Your Name  
Course Number: Course Name  
Month Day, Year
:::

:::

{{< pagebreak >}}

:::


<!-- ============================================================
TITLE PAGE — TYPST
=============================================================== -->

::: {.content-visible when-format="typst"}

```{=typst}
#set page(numbering: none)

#v(30%)

#align(center)[
Your Paper Title

#v(192pt)

Your Name \
Course Number: Course Name \
Month Day, Year
]

#pagebreak()

#counter(page).update(1)

#set page(
  numbering: "1",
  number-align: right + top
)
```

:::


<!-- ============================================================
BODY
=============================================================== -->

Start writing your paper here. Normal body text is 12-point Times New
Roman, double-spaced, with one-inch margins in paged document formats
and a half-inch first-line paragraph indent.

A standard Chicago 18 author-date citation looks like this
[@smith2024, 42].

Another source can be cited like this [@jones2022, 220].

For a narrative citation, @smith2024 [42] argues that the evidence
supports this interpretation.

This is another paragraph so you can verify ordinary paragraph
indentation and line spacing.

```{r}
if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman")

library(pacman)

pacman::p_load(
  ggplot2,
  ggtext
)

knitr::opts_chunk$set(dev = "ragg_png")
```


```{r}
# https://advance.lexis.com/api/permalink/5bbd017c-bb50-4cb5-a4fa-0d2066a1d2de/?context=1519360&identityprofileid=BQ226N51782

DATA_FILE <- "CoverageoverTime_FlockcameraORFlockcamerasORFlockSafety.csv"

lexis_coverage_raw <- read.csv2(
  DATA_FILE,
  check.names = FALSE,
  fileEncoding = "UTF-8-BOM"
)

lexis_coverage_monthly <- data.frame(
  month = as.Date(substr(
    lexis_coverage_raw[["Coverage over Time"]], 1, 10
  )),
  articles = as.integer(lexis_coverage_raw[["Coverage"]])
)

lexis_coverage_complete <- subset(
  lexis_coverage_monthly,
  month <= as.Date("2026-08-01")
)

lexis_coverage_september_segment <- subset(
  lexis_coverage_monthly,
  month >= as.Date("2026-08-01")
)

lexis_coverage_september <- subset(
  lexis_coverage_monthly,
  month == as.Date("2026-09-01")
)

plot_lexis_coverage_monthly <- ggplot(
  lexis_coverage_monthly,
  aes(x = month, y = articles)
) +
  geom_line(
    data = lexis_coverage_complete,
    color = "#00A693",
    linewidth = 1
  ) +
  geom_line(
    data = lexis_coverage_september_segment,
    color = "#00A693",
    linewidth = 1,
    linetype = "dashed"
  ) +
  geom_point(
    data = lexis_coverage_complete,
    color = "#00A693",
    size = 2.3
  ) +
  geom_point(
    data = lexis_coverage_september,
    color = "#00A693",
    fill = "white",
    shape = 21,
    size = 2.8,
    stroke = 1
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  scale_y_continuous(
    breaks = c(
      min(lexis_coverage_monthly$articles),
      1000, 2000, 3000, 4000
    ),
    labels = scales::label_comma(),
    limits = c(min(lexis_coverage_monthly$articles), 4500),
    expand = expansion(mult = c(0, 0))
  ) +
  coord_cartesian(clip = "off") +
  labs(
    title = paste(
      "News Articles Mentioning Flock",
      sep = "\n"
    ),
    subtitle = "Monthly Counts From a Nexis Uni News Search",
    x = NULL,
    y = "Number of Articles",
    caption = paste(
      "<b>Source:</b> Nexis Uni Analytics Export",
      "<b>Search Terms:</b> Flock camera or Flock cameras or Flock Safety",
      "<b>Note:</b> The dashed segment and open circle mark incomplete September results through September 27, 2026.",
      sep = "<br>"
    )
  ) +
  theme_minimal(
    base_family = "Georgia",
    base_size = 11
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.caption = ggtext::element_markdown(hjust = 0, size = 9),
    plot.caption.position = "plot"
  )

print(plot_lexis_coverage_monthly)

ggsave(
  file.path(dirname(DATA_FILE), "Coverage_Over_Time_Monthly.png"),
  plot = plot_lexis_coverage_monthly,
  width = 8.88,
  height = 5.5,
  units = "in",
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
# https://trends.google.com/explore?q=flock&date=2026-01-01%202026-09-27&geo=US

DATA_FILE2 <- "time_series_US_20260101-0000_20260927-1417.csv"

google_trends_raw <- read.csv(
  DATA_FILE2,
  check.names = FALSE,
  fileEncoding = "UTF-8-BOM"
)

google_trends_weekly <- data.frame(
  week = as.Date(google_trends_raw[["Time"]]),
  search_interest = as.integer(google_trends_raw[["flock"]])
)

google_trends_weekly_by_day <- do.call(
  rbind,
  lapply(seq_len(nrow(google_trends_weekly)), function(i) {
    data.frame(
      date = seq(
        google_trends_weekly$week[i],
        google_trends_weekly$week[i] + 6,
        by = "day"
      ),
      search_interest = google_trends_weekly$search_interest[i]
    )
  })
)

google_trends_weekly_by_day <- subset(
  google_trends_weekly_by_day,
  date >= as.Date("2026-01-01") &
    date <= as.Date("2026-09-27")
)

google_trends_weekly_by_day$month <- as.Date(paste0(
  format(google_trends_weekly_by_day$date, "%Y-%m"),
  "-01"
))

google_trends_monthly <- aggregate(
  search_interest ~ month,
  data = google_trends_weekly_by_day,
  FUN = mean
)

google_trends_monthly$month_label <- factor(
  format(google_trends_monthly$month, "%b %Y"),
  levels = format(
    seq(as.Date("2026-01-01"), as.Date("2026-09-01"), by = "month"),
    "%b %Y"
  )
)

google_trends_complete_months <- subset(
  google_trends_monthly,
  month <= as.Date("2026-08-01")
)

google_trends_september_segment <- subset(
  google_trends_monthly,
  month >= as.Date("2026-08-01")
)

google_trends_september <- subset(
  google_trends_monthly,
  month == as.Date("2026-09-01")
)

plot_google_trends_monthly <- ggplot(
  google_trends_monthly,
  aes(x = month_label, y = search_interest, group = 1)
) +
  geom_line(
    data = google_trends_complete_months,
    color = "#00A693",
    linewidth = 1
  ) +
  geom_line(
    data = google_trends_september_segment,
    color = "#00A693",
    linewidth = 1,
    linetype = "dashed"
  ) +
  geom_point(
    data = google_trends_complete_months,
    color = "#00A693",
    size = 2.3
  ) +
  geom_point(
    data = google_trends_september,
    color = "#00A693",
    fill = "white",
    shape = 21,
    size = 2.8,
    stroke = 1
  ) +
  scale_x_discrete(
    drop = FALSE,
    expand = expansion(add = 0.2)
  ) +
  scale_y_continuous(
    breaks = c(0, 25, 50, 75, 100),
    limits = c(0, 100),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Google Search Interest in 'flock'",
    subtitle = "Monthly Averages of Weekly Scores in the United States",
    x = NULL,
    y = "Relative Search Interest (0–100)",
    caption = paste(
      "<b>Source:</b> Google Trends, United States",
      "<b>Search Term:</b> flock",
      "<b>Method:</b> Weekly scores are weighted by the days they cover in each month.",
      "<b>Note:</b> The dashed line and open circle mark September, which includes data through September 27, 2026.",
      sep = "<br>"
    )
  ) +
  theme_minimal(
    base_family = "Georgia",
    base_size = 11
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.caption = ggtext::element_markdown(hjust = 0, size = 9),
    plot.caption.position = "plot"
  )

print(plot_google_trends_monthly)

ggsave(
  file.path(dirname(DATA_FILE2), "Google_Search_Interest_Flock_Monthly.png"),
  plot = plot_google_trends_monthly,
  width = 8.88,
  height = 5.5,
  units = "in",
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
library(ggplot2)

# Published percentages:
# https://yougov.com/en-us/daily-results/20250904-67d37-1
# https://yougov.com/en-us/daily-results/20260824-a9b53-1
# https://www.filesforprogress.org/datasets/2026/9/dfp_flock_cameras_tabs.pdf

OUTPUT_DIRECTORY <- "/Users/anton/Downloads"

yougov_license_plate_reader_percentages <- data.frame(
  response_category = factor(
    rep(c("Support", "Oppose", "Not Sure"), times = 2),
    levels = c("Support", "Oppose", "Not Sure")
  ),
  survey_label = factor(
    rep(c("Sep 2025", "Aug 2026"), each = 3),
    levels = c("Sep 2025", "Aug 2026")
  ),
  response_percentage = c(45, 33, 21, 38, 46, 17)
)

plot_yougov_license_plate_reader_opinions <- ggplot(
  yougov_license_plate_reader_percentages,
  aes(x = response_category, y = response_percentage, fill = survey_label)
) +
  geom_col(
    position = position_dodge(width = 0.7),
    width = 0.58
  ) +
  geom_text(
    aes(label = paste0(response_percentage, "%")),
    position = position_dodge(width = 0.7),
    vjust = -0.45,
    family = "Georgia",
    size = 3.5
  ) +
  scale_fill_manual(
    values = c("Sep 2025" = "#98A6AD", "Aug 2026" = "#00A693")
  ) +
  scale_x_discrete(
    expand = expansion(add = 0.4)
  ) +
  scale_y_continuous(
    breaks = c(0, 10, 20, 30, 40, 50),
    labels = function(x) paste0(x, "%"),
    limits = c(0, 55),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Opinions on Using Automated License Plate Readers for Law Enforcement",
    subtitle = "YouGov Surveys of U.S. Adults, September 2025 and August 2026",
    x = NULL,
    y = "Percent of U.S. Adults",
    fill = NULL,
    caption = paste(
      "<b>Source:</b> YouGov Daily Questions (Sep 4, 2025: n = 8,832; Aug 24, 2026: n = 20,563).",
      "<b>Question:</b> Support or oppose automated license plate readers for law enforcement in your community.",
      "<b>Note:</b> Support and oppose combine strongly and somewhat responses. Totals may differ from 100% because of rounding.",
      sep = "<br>"
    )
  ) +
  theme_minimal(
    base_family = "Georgia",
    base_size = 11
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.caption = ggtext::element_markdown(hjust = 0, size = 9),
    plot.caption.position = "plot"
  )

print(plot_yougov_license_plate_reader_opinions)

ggsave(
  file.path(dirname(DATA_FILE2), "YouGov_ALPR_Poll_2025_2026.png"),
  plot = plot_yougov_license_plate_reader_opinions,
  width = 8.88,
  height = 5.5,
  units = "in",
  dpi = 300,
  device = ragg::agg_png
)

data_for_progress_flock_percentages <- data.frame(
  survey_start = as.Date(c("2026-08-21", "2026-09-11", "2026-09-18")),
  survey_label = c("Aug 21–24", "Sep 11–14", "Sep 18–20"),
  unfavorable_percentage = c(41, 47, 52)
)

plot_data_for_progress_flock_unfavorable <- ggplot(
  data_for_progress_flock_percentages,
  aes(x = survey_start, y = unfavorable_percentage)
) +
  geom_line(color = "#00A693", linewidth = 1) +
  geom_point(color = "#00A693", size = 2.3) +
  geom_text(
    aes(label = paste0(unfavorable_percentage, "%")),
    vjust = -0.8,
    family = "Georgia",
    size = 3.5
  ) +
  scale_x_date(
    breaks = data_for_progress_flock_percentages$survey_start,
    labels = data_for_progress_flock_percentages$survey_label,
    limits = as.Date(c("2026-08-17", "2026-09-22")),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_y_continuous(
    breaks = c(0, 20, 40, 60),
    labels = function(x) paste0(x, "%"),
    limits = c(0, 60),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Unfavorable Views of Flock Cameras",
    subtitle = "Data for Progress Surveys of U.S. Likely Voters, August–September 2026",
    x = NULL,
    y = "Percent Unfavorable",
    caption = paste(
      "<b>Source:</b> Data for Progress survey tables (Aug 21–24: n = 1,175; Sep 11–14: n = 1,214; Sep 18–20: n = 1,194).",
      "<b>Question:</b> Favorable or unfavorable view of Flock Safety surveillance cameras.",
      "<b>Note:</b> Each point represents a separate survey of likely voters; dates show fieldwork periods.",
      sep = "<br>"
    )
  ) +
  theme_minimal(
    base_family = "Georgia",
    base_size = 11
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.caption = ggtext::element_markdown(hjust = 0, size = 9),
    plot.caption.position = "plot"
  )

print(plot_data_for_progress_flock_unfavorable)

ggsave(
  file.path(dirname(DATA_FILE2), "Data_For_Progress_Flock_Poll_Aug_Sep_2026.png"),
  plot = plot_data_for_progress_flock_unfavorable,
  width = 8.88,
  height = 5.5,
  units = "in",
  dpi = 300,
  device = ragg::agg_png
)

```

<!-- ============================================================
LEVEL 1
Centered
Bold
Headline-Style Capitalization
=============================================================== -->

# Contemporary Literature

This demonstrates a Level 1 heading.


<!-- ============================================================
LEVEL 2
Centered
Regular
Headline-Style Capitalization
=============================================================== -->

## What Are the Major Movements?

This demonstrates a Level 2 heading.


<!-- ============================================================
LEVEL 3
Flush left
Italic
Headline-Style Capitalization
=============================================================== -->

### Beat Generation

This demonstrates a Level 3 heading.


<!-- ============================================================
LEVEL 4
Flush left
Regular
Sentence-style capitalization
=============================================================== -->

#### Significant figures, events, and elements

This demonstrates a Level 4 heading.


<!-- ============================================================
LEVEL 5

For reliable visual consistency across PDF, Word, ODT,
HTML, EPUB, and Typst, write Level 5 directly at the
start of the paragraph in italics with a terminal period.

This avoids Word treating Heading 5 as a separate block.
=============================================================== -->

*Kerouac as the leader.* The role of founding Beat Generation poet was
filled by Jack Kerouac. This Level 5 heading remains run-in across the
major output formats.


<!-- ============================================================
BLOCK QUOTATION
=============================================================== -->

# Block Quotation Example

Normal double-spaced body text appears before the block quotation.

> This is an example of a block quotation. A prose quotation of five or
> more lines or more than one hundred words should be blocked. It begins
> on a new line, appears without quotation marks, is indented from the
> left margin, and is single-spaced. [@smith2024, 50]

Normal double-spaced body text resumes here.


<!-- ============================================================
CONCLUSION
=============================================================== -->

# Conclusion

Write your conclusion here.


<!-- ============================================================
REFERENCES — PDF
=============================================================== -->

::: {.content-visible when-format="pdf"}

```{=latex}
\newpage

\begin{singlespace}

\noindent\makebox[\textwidth][c]{References}\par

% Two blank lines between heading and first entry.

\vspace{2\baselineskip}
```

:::


<!-- ============================================================
REFERENCES — WORD
=============================================================== -->

::: {.content-visible when-format="docx"}

{{< pagebreak >}}

::: {custom-style="CMOS References Heading"}
References
:::

:::


<!-- ============================================================
REFERENCES — ODT
=============================================================== -->

::: {.content-visible when-format="odt"}

{{< pagebreak >}}

::: {custom-style="CMOS References Heading"}
References
:::

:::


<!-- ============================================================
REFERENCES — HTML / EPUB
=============================================================== -->

::: {.content-visible when-format="html"}

{{< pagebreak >}}

::: {.cmos-references-heading}
References
:::

:::


<!-- ============================================================
REFERENCES — TYPST
=============================================================== -->

::: {.content-visible when-format="typst"}

```{=typst}
#pagebreak()
#align(center)[References]
#v(2em)
```

:::


<!-- ============================================================
CITATION PROCESSOR INSERTS REFERENCES HERE
=============================================================== -->

::: {#refs}
:::


<!-- ============================================================
END PDF REFERENCE SPACING
=============================================================== -->

::: {.content-visible when-format="pdf"}

```{=latex}
\end{singlespace}
```

:::


<!-- ============================================================
OPTIONAL FOOTNOTES
===============================================================

Author-Date papers may still use footnotes for supplemental commentary.

Quarto syntax:

Here is a sentence with a supplemental note.^[This is the footnote text.]

=============================================================== -->


<!-- ============================================================
TABLES AND FIGURES
===============================================================

Place tables and figures as soon as practical after they are first
mentioned.

For figures, include a figure number and caption.

If material is reproduced or adapted from another source, provide
an appropriate source or credit line and include the source in the
References list when applicable.

=============================================================== -->


<!-- ============================================================
CHECKLIST
===============================================================

BODY
- Times New Roman, 12 pt
- 1-inch margins in paged formats
- Double-spaced normal body text
- 0.5-inch first-line indent
- No extra paragraph spacing

PDF PAGINATION
- No visible number on title page
- First actual text page = Arabic 1
- Page number upper right

WORD PAGINATION
- Controlled by cmos-reference.docx
- Different First Page enabled
- Title page header blank
- Subsequent page numbers upper right
- First text page displays 1

TITLE PAGE
- Title approximately one-third down page
- Regular 12-point type
- Not all caps
- Identifying information several lines later
- Eight-baseline PDF gap is a visual implementation choice

HEADINGS
- Level 1: centered, bold
- Level 2: centered, regular
- Level 3: flush left, italic
- Level 4: flush left, regular
- Level 5: run-in, italic, terminal period

BLOCK QUOTATIONS
- New line
- No quotation marks
- Single spaced
- 0.5-inch left indent

REFERENCES
- Heading = References
- Heading centered
- Two blank lines before first entry
- Entries single spaced internally
- One blank line between entries
- 0.5-inch hanging indent
- Chicago author-date CSL handles bibliography formatting

=============================================================== -->